Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi Testbed

### 2016-06-12 raspi_journal.tex
Updating metainfo and paper description
Removing redundant sections

%=================================================================
% Full title of the paper (Capitalized)
\Title{Easy as Pi: A Network Coding Raspberry Pi Testbed}

% Authors, for the paper (add full first names)
\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3,4}$, Simon Wunderlich $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
% Authors, for metadata in PDF
\AuthorNames{Nestor Hernandez, Chres W. Soerensen, Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks. Dresden, Germany; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
$^{4}$ \quad SFB 912 -- Collaborative Research Center HAEC. Dresden, Germany}

@@

\section{Testbed Description}
\input{testbed}

\section{Cross-compilation: From PC to Raspberry Pi}
\input{cross_compilation}

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in
the Raspberry Pi Testbed}

% Authors, for the paper (add full first names)
\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3,4}$, Simon Wunderlich $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
% Authors, for metadata in PDF
\AuthorNames{Chres W. Soerensen, Nestor J. Hernandez M., Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks. Dresden, Germany; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
$^{4}$ \quad SFB 912 -- Collaborative Research Center HAEC. Dresden, Germany}

@@

% \section{Testbed Description}
% \input{testbed}

% \section{Cross-compilation: From PC to Raspberry Pi}
% \input{cross_compilation}
